Jaigo Technical Report

### 2007-12-19 paper/paper.tex
todo

\usepackage{hyperref}
\usepackage{memhfixc}

@@

\tableofcontents
\listoftables

\chapter{Introduction}
%Include background materials and define the problem and scope of your project.
Go is a two-player board game which originated in Ancient China and remains one of the most richly complex games of strategy today. The objective is to control more area or territory than one's opponent on the game board. The game is played on a square line grid; the standard size of this grid is 19 x 19, though 13 x 13 and 9 x 9 grids are used occasionally. Players place stones -- either black or white -- at the intersecting points of the grid to signify control of that position. Once placed on the board a stone has a number of liberties -- unoccupied grid positions which are orthogonally adjacent to that stone. The goal of the game is to claim as much territory as possible by forming chains (contiguous extensions of stones of the same color) which cannot be captured by one's opponent. A stone or chain is captured and removed from the board when it has no liberties, the result of being surrounded by stones of the opposing color.

@@

We chose to implement two different move choice engines, each of which provides a different playing experience. SimpleGo v1, a 50kyu greedy search move generator which picks a random move from list of moves with worst opponent score. Crawler, an unranked move generator which analyzes the current blocks on the board and picks the move that both connects to a block and results in the largest number of liberties for the block.

\chapter{Technical details}
Code Listing
- Implementation of Benson's algorithm for determining unconditional life: Analyze\_Color\_Unconditional\_Status
- Greedy Search algorithm: select\_scored\_move
- Crawler algorithm: select\_crawler\_move

\chapter{Discussions, observations, and comparisons}
We implemented two move choice engines based on two different algorithms, scoring for color and blocks based on Benson's algorithm, and representations of the board, the game, eyes, blocks, and numerous language-specific utilities. Our goals were compactness and speed due to the target platform limitations.

@@

For the first 50 moves on a 19x19 board with human (black) versus crawler (white),
$\begin{tabular}{ccccccccc}
\hline
Function & Calls & Percent & Own Time & Time & Avg & Min & Max & File\\
\hline
(no name) & 109675 & 25.68% & 14310.594ms &	36908.812ms &	0.337ms &	0.059ms	& 1593.542ms	& simple_go.js (line 407)\\
\hline
flood_mark & 1618 & 14.17% & 7897.73ms & 25481.245ms & 15.749ms & 0.162ms & 1635.18ms & simple_go.js (line 807)\\
\hline
(no name) &	194678 &	11.75%	& 6551.626ms &	6554.733ms &	0.034ms &	0.008ms &	1555.243ms &	simple_go.js (line 819)\\
\hline
string_as_move &	56065 &	7.48% &	4168.485ms &	4169.549ms &	0.074ms &	0.011ms &	1591.844ms &	simple_go.js (line 192)\\
\hline
iterate	109676 &	7.19% &	4005.749ms &	22595.463ms &	0.206ms &	0.011ms &	1593.499ms &	simple_go.js (line 391)\\
\hline
(no name) &	283642 &	4.9% &	2732.499ms &	18589.343ms &	0.066ms &	0.015ms &	1593.144ms &	simple_go.js & (line 416)\\
\hline
iterateOwnProperties &	5811	& 4.38%	& 2440.378ms &	2847.852ms &	0.49ms &	0.004ms &	2.917ms &	simple_go.js (line 132)\\
\hline
Set_Goban &	2150 &	3.53% &	1968.651ms &	1969.095ms &	0.916ms &	0.004ms &	942.058ms &	simple_go.js (line 528)\\
\hline
(no name) &	42734 &	2.99% &	1666.478ms &	1666.716ms &	0.039ms &	0.008ms &	935.83ms &	simple_go.js (line 835)\\
\hline
update &	3662 &	2.9% &	1613.61ms &	1614.099ms &	0.441ms &	0.004ms &	1560.416ms &	simple_go.js (line 117)\\
\hline
Add_Block &	2340 &	2.8% &	1559.92ms &	1560.774ms &	0.667ms &	0.007ms &	1529.63ms &	simple_go.js (line 757)\\
\hline
Calculate_Neighbour &	448	2.67% &	1487.337ms &	12205.939ms &	27.245ms &	0.019ms &	1579.849ms &	simple_go.js (line 829)\\
\hline
Simple_Same_Block &	2149 &	1.93% &	1073.573ms &	8185.472ms &	3.809ms &	0.002ms &	1556.376ms &	simple_go.js (line 606)\\
\hline
List_Block_Liberties &	3210 &	1.56% &	871.609ms &	5057.619ms &	1.576ms &	0.012ms &	1593.058ms &	simple_go.js (line 863)\\
\hline
\end{tabular}

For the first 100 moves of a game on a 19x19 board, with crawler (black) versus crawler (white),

\begin{tabular}{ccccccccc}
	\hline
	Function & Calls & Percent & Own Time & Time & Avg & Min & Max & File\\	
\hline
(no name) &	$404494 &	32.8% &	71255.203ms &	147518.241ms &	0.365ms &	0.059ms &	1650.149ms &	simple_go.js (line 407)\\
\hline
flood_mark &	3838 &	15.94% &	34634.022ms &	96713.52ms &	25.199ms &	0.206ms &	1736.537ms &	simple_go.js (line 807)\\
\hline
iterate &	404495 &	8.75% &	19004.696ms &	76254.33ms &	0.189ms &	0.011ms &	1650.101ms &	simple_go.js (line 391)\\
\hline
(no name) &	735190 &	8.72% &	18941.197ms &	18941.987ms &	0.026ms &	0.008ms &	1572.648ms &	simple_go.js (line 819)\\
\hline
string_as_move &	242765 &	5.86% &	12724.373ms	& 12725.279ms &	0.052ms &	0.011ms &	1629.186ms &	simple_go.js (line 192)\\
\hline
(no name) &	1041519 &	4.7% &	10209.513ms &	57248.372ms &	0.055ms &	0.015ms &	1649.869ms &	simple_go.js (line 416)\\
\hline
List_Block_Liberties &	7706 &	4.02% &	8727.331ms &	21457.809ms &	2.785ms &	0.013ms &	1630.607ms &	simple_go.js (line 863)\\
\hline
iterateOwnProperties &	14752 &	3.68% &	7985.019ms &	9340.503ms &	0.633ms &	0.004ms &	2.419ms &	simple_go.js (line 132)\\
\hline
update &	8742 &	3.18% &	6911.102ms &	6911.93ms &	0.791ms &	0.004ms &	1648.007ms &	simple_go.js (line 117)\\
\hline
Calculate_Neighbour &	661 &	3.03% &	6593.032ms &	60385.478ms &	91.355ms &	0.115ms &	1679.244ms &	simple_go.js (line 829)\\
\hline
(no name) &	160414 &	2.51% &	5444.827ms &	5445.809ms &	0.034ms	& 0.008ms &	944.464ms &	simple_go.js (line 835)\\
\hline
Add_Stone &	6010 &	1.1% &	2392.214ms	& 191461.602ms	& 31.857ms &	1.524ms &	1785.447ms &	simple_go.js (line 641)\\
\hline
\end{tabular}

@@

On an iPhone over 54mbps 802.11g wifi with a full signal connected to a 3mbps cable modem, the median jaigo load time was 5 seconds, with the initial load time being the longest measurement at 15 seconds. On an iPhone over AT&T 2.5G EDGE with a full signal, the median jaigo load time was 21 seconds, with a low of 17 seconds and a high of 30 seconds.

Median move times in other go engines (gnugo especially)?

\chapter{Recommendations, especially for future work and unsolved issues}
We feel that the choice of browser is more important than the choice of computing platform for the performance of jaigo. However, we have not quantified this claim.

>>>>

\usepackage{listings}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{memhfixc}

@@

\tableofcontents
\listoftables
\lstlistoflistings

\mainmatter
\chapter{Introduction}
%Include background materials and define the problem and scope of your project.
Go is a two-player board game which originated in Ancient China and remains one of the most richly complex games of strategy today. The objective is to control more area or territory than one's opponent on the game board. The game is played on a square line grid; the standard size of this grid is 19 x 19, though 13 x 13 and 9 x 9 grids are used occasionally. Players place stones -- either black or white -- at the intersecting points of the grid to signify control of that position. Once placed on the board a stone has a number of liberties -- unoccupied grid positions which are orthogonally adjacent to that stone. The goal of the game is to claim as much territory as possible by forming chains (contiguous extensions of stones of the same color) which cannot be captured by one's opponent. A stone or chain is captured and removed from the board when it has no liberties, the result of being surrounded by stones of the opposing color.

@@

We implemented two different move choice engines, each of which provides a different playing experience. SimpleGo v1, a 50kyu greedy search move generator which picks a random move from list of moves with worst opponent score. Crawler, an unranked move generator which analyzes the current blocks on the board and picks the move that both connects to a block and results in the largest number of liberties for the block.

\chapter{Technical details}
%Code Listing
\lstset{language=Java,breaklines=true}% if I have extra time, I'll define JavaScript for real
\lstinputlisting[label={code:benson}, caption={Benson's Algorithm}]{benson.js}
\lstinputlisting[label={code:greedy}, caption={Move generator: greedy search}]{greedy.js}
\lstinputlisting[label={code:crawler}, caption={Move generator: crawler}]{crawler.js}

\chapter{Discussions, observations, and comparisons}
We implemented representations of the board, the game, eyes, and blocks; scoring for color and blocks based on Benson's algorithm; two move choice engines based on two different algorithms; and numerous language-specific utilities. Our goals were compactness and speed due to the target platform limitations.

@@

\tref{table:first50} shows the first 50 moves on a 19x19 board with human (black) versus crawler (white).
\begin{table}
  \rotatebox{90}{
    \begin{tabular}{ccccccccc} \toprule
      Function & Calls & Percent & Own Time (ms) & Time (ms) & Avg (ms) & Min (ms) & Max (ms) & File\\ \midrule
      (no name) & 109675 & 25.68 & 14310.594 &	36908.812 &	0.337 &	0.059	& 1593.542	& simple\_go.js (line 407)\\
      flood\_mark & 1618 & 14.17 & 7897.73 & 25481.245 & 15.749 & 0.162 & 1635.18 & simple\_go.js (line 807)\\
      (no name) &	194678 &	11.75	& 6551.626 &	6554.733 &	0.034 &	0.008 &	1555.243 &	simple\_go.js (line 819)\\
      string\_as\_move &	56065 &	7.48 &	4168.485 &	4169.549 &	0.074 &	0.011 &	1591.844 &	simple\_go.js (line 192)\\
      iterate	& 109676 &	7.19 &	4005.749 &	22595.463 &	0.206 &	0.011 &	1593.499 &	simple\_go.js (line 391)\\
      (no name) &	283642 &	4.9 &	2732.499 &	18589.343 &	0.066 &	0.015 &	1593.144 &	simple\_go.js (line 416)\\
      iterateOwnProperties &	5811	& 4.38	& 2440.378 &	2847.852 &	0.49 &	0.004 &	2.917 &	simple\_go.js (line 132)\\
      Set\_Goban &	2150 &	3.53 &	1968.651 &	1969.095 &	0.916 &	0.004 &	942.058 &	simple\_go.js (line 528)\\
      (no name) &	42734 &	2.99 &	1666.478 &	1666.716 &	0.039 &	0.008 &	935.83 &	simple\_go.js (line 835)\\
      update &	3662 &	2.9 &	1613.61 &	1614.099 &	0.441 &	0.004 &	1560.416 &	simple\_go.js (line 117)\\
      Add\_Block &	2340 &	2.8 &	1559.92 &	1560.774 &	0.667 &	0.007 &	1529.63 &	simple\_go.js (line 757)\\
      Calculate\_Neighbour &	448 &	2.67 &	1487.337 &	12205.939 &	27.245 &	0.019 &	1579.849 &	simple\_go.js (line 829)\\
      Simple\_Same\_Block &	2149 &	1.93 &	1073.573 &	8185.472 &	3.809 &	0.002 &	1556.376 &	simple\_go.js (line 606)\\
      List\_Block\_Liberties &	3210 &	1.56 &	871.609 &	5057.619 &	1.576 &	0.012 &	1593.058 &	simple\_go.js (line 863)\\ \bottomrule
  \end{tabular}}
  \caption{First 50 moves on a 19x19 board}
  \label{table:first50}
\end{table}

\tref{table:first100} shows the first 100 moves of a game on a 19x19 board, with crawler (black) versus crawler (white).

\begin{table}
  \rotatebox{90}{
    \begin{tabular}{ccccccccc} \toprule
      Function & Calls & Percent & Own Time & Time & Avg & Min & Max & File\\	\midrule
      (no name) &	404494 &	32.8 &	71255.203 &	147518.241 &	0.365 &	0.059 &	1650.149 &	simple\_go.js (line 407)\\
      flood\_mark &	3838 &	15.94 &	34634.022 &	96713.52 &	25.199 &	0.206 &	1736.537 &	simple\_go.js (line 807)\\
      iterate &	404495 &	8.75 &	19004.696 &	76254.33 &	0.189 &	0.011 &	1650.101 &	simple\_go.js (line 391)\\
      (no name) &	735190 &	8.72 &	18941.197 &	18941.987 &	0.026 &	0.008 &	1572.648 &	simple\_go.js (line 819)\\
      string\_as\_move &	242765 &	5.86 &	12724.373	& 12725.279 &	0.052 &	0.011 &	1629.186 &	simple\_go.js (line 192)\\
      (no name) &	1041519 &	4.7 &	10209.513 &	57248.372 &	0.055 &	0.015 &	1649.869 &	simple\_go.js (line 416)\\
      List\_Block\_Liberties &	7706 &	4.02 &	8727.331 &	21457.809 &	2.785 &	0.013 &	1630.607 &	simple\_go.js (line 863)\\
      iterateOwnProperties &	14752 &	3.68 &	7985.019 &	9340.503 &	0.633 &	0.004 &	2.419 &	simple\_go.js (line 132)\\
      update &	8742 &	3.18 &	6911.102 &	6911.93 &	0.791 &	0.004 &	1648.007 &	simple\_go.js (line 117)\\
      Calculate\_Neighbour &	661 &	3.03 &	6593.032 &	60385.478 &	91.355 &	0.115 &	1679.244 &	simple\_go.js (line 829)\\
      (no name) &	160414 &	2.51 &	5444.827 &	5445.809 &	0.034	& 0.008 &	944.464 &	simple\_go.js (line 835)\\
      Add\_Stone &	6010 &	1.1 &	2392.214	& 191461.602	& 31.857 &	1.524 &	1785.447 &	simple\_go.js (line 641)\\ \bottomrule
    \end{tabular}}
  \caption{First 100 moves on a 19x19 board}
  \label{table:first100}
\end{table}

@@

On an iPhone over 54mbps 802.11g wifi with a full signal connected to a 3mbps cable modem, the median jaigo load time was 5 seconds, with the initial load time being the longest measurement at 15 seconds. On an iPhone over AT\&T 2.5G EDGE with a full signal, the median jaigo load time was 21 seconds, with a low of 17 seconds and a high of 30 seconds.
%TODO: Median move times in other go engines (gnugo especially)?

\chapter{Recommendations, especially for future work and unsolved issues}
We feel that the choice of browser is more important than the choice of computing platform for the performance of jaigo. Our anecdotal experience and those of others on the Web show that there is an order of magnitude difference between popular browsers for some JavaScript operations. However, we have not carefully studied this issue.%http://therealcrisp.xs4all.nl/blog/2006/12/09/string-performance-in-internet-explorer/
